Assessment of the ability to track changes for nowcasts, measurements, and forecasts

### 2024-04-10 paper.tex
Update on Overleaf.

\abstract{ % Weniger We; Erste zwei Sätze kombinieren
In addition to the numerical precision, the direction of change alone is easily and intuitively interpretable information on the development.
We consider whether measurements, nowcasts, and forecasts are able to correctly indicate the direction of change of a value of interest.
We refer to the ability to predict the right direction of development as the ability to track changes.

>>>>

\abstract{ % Weniger We; Erste zwei Sätze kombinieren
In addition to the numerical precision of measurements, nowcasts, and forecasts, their ability to reflect changes in the underlying values can be crucial in applications.
We refer to the ability to predict the right direction of development as the ability to track changes and present visual techniques and quantitative measures to assess this ability.
We provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
Three medical or healthcare problems illustrate the assessment: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.

In addition to the numerical precision, the direction of change alone is easily and intuitively interpretable information on the development of a value of interest.
We consider whether measurements, nowcasts, and forecasts are able to correctly indicate the direction of change of a value of interest.
